*Supplementary Material 2*

### 2022-06-20 ms/si2.Rmd
Add dagger for extinct taxa

# Trim this R script down to only functions that define figure and table captions
read_lines(temp_file) %>%
  magrittr::extract(
    str_detect(., "^figure\\(|^table\\(|^s_figure\\(|^s_table\\(|^figure_num\\(|^table_num\\(|^s_figure_num\\(|^s_table_num\\(")
  ) %>%
  unique %>%
  write_lines(temp_file)

@@

```{r tidy-fossil-data}
# Add category to metadata
fossil_meta <-
  fossil_meta %>%
  mutate(
    category = case_when(
      variable %in% colnames(fossil_ferns_raw)[1:4] ~ "Calibration",
      variable %in% colnames(fossil_ferns_raw)[5:12] ~ "Fossil Identity",
      variable %in% colnames(fossil_ferns_raw)[13:18] ~ "Fossil Age",
      variable %in% colnames(fossil_ferns_raw)[19:21] ~ "Fossil Locality",
      variable %in% colnames(fossil_ferns_raw)[22:24] ~ "Fossil Specimen",
      TRUE ~ NA_character_
    ),
    var_order = 1:nrow(.)
  )

@@

# Tidy fossils in wide format
fossils_long <-
  fossil_ferns_raw %>%
  # Filter to only those actually used in the study
  inner_join(
    n_fos_used, by = "n_fos"
  ) %>%
  verify(all(sort(.$n_fos) == sort(n_fos_used$n_fos))) %>%
  mutate(
    across(everything(), as.character),
    # Add fossil taxon header
    fossil_taxon_header = fossil_taxon) %>%
  pivot_longer(names_to = "variable", values_to = "value", -fossil_taxon) %>%
  left_join(
    select(fossil_meta, -description), by = "variable") %>%
  mutate(
    text = as.character(glue::glue("{formatted_name}: {value}"))
  ) %>%
  arrange(fossil_taxon, category, var_order) %>%
  # Drop NA entries
  filter(!is.na(value))
```

These data are exported from the FernCal v1.0.0 database (https://github.com/fernphy/ferncal), which includes records of fossils to use as calibration points for molecular dating of ferns.

>>>>

# Trim this R script down to only functions that define figure and table captions
read_lines(temp_file) %>%
  magrittr::extract(
    str_detect(
      .,
    "^figure\\(|^table\\(|^s_figure\\(|^s_table\\(|^figure_num\\(|^table_num\\(|^s_figure_num\\(|^s_table_num\\(" # nolint
    )
  ) %>%
  unique %>%
  write_lines(temp_file)

@@

```{r tidy-fossil-data}
# Add category to metadata
fossil_meta <-
  fossil_meta %>%
  mutate(
    category = case_when(
      variable %in% colnames(fossil_ferns_raw)[1:4] ~ "Calibration",
      variable %in% colnames(fossil_ferns_raw)[5:13] ~ "Fossil Identity",
      variable %in% colnames(fossil_ferns_raw)[14:19] ~ "Fossil Age",
      variable %in% colnames(fossil_ferns_raw)[20:22] ~ "Fossil Locality",
      variable %in% colnames(fossil_ferns_raw)[23:25] ~ "Fossil Specimen",
      TRUE ~ NA_character_
    ),
    var_order = seq_along(variable)
  )

@@

# Tidy fossils in wide format
fossils_long <-
  fossil_ferns_raw %>%
  # Filter to only those actually used in the study
  inner_join(
    n_fos_used, by = "n_fos"
  ) %>%
  verify(all(sort(.$n_fos) == sort(n_fos_used$n_fos))) %>%
  mutate(
    across(everything(), as.character),
    extinct = case_when(
      extinct == "extinct" ~ "^†^",
      extinct == "extant" ~ "",
      TRUE ~ NA_character_
    )) %>%
  assert(not_na, extinct, fossil_taxon) %>%
  # Add fossil taxon header
  mutate(fossil_taxon_header = glue::glue("{fossil_taxon}{extinct}")) %>%
  pivot_longer(names_to = "variable", values_to = "value", -fossil_taxon) %>%
  left_join(
    select(fossil_meta, -description), by = "variable") %>%
  mutate(
    text = as.character(glue::glue("{formatted_name}: {value}"))
  ) %>%
  arrange(fossil_taxon, category, var_order) %>%
  # Drop NA entries
  filter(!is.na(value)) %>%
  filter(variable != "extinct")
```

These data are exported from the FernCal v1.0.1 database (https://github.com/fernphy/ferncal), which includes records of fossils to use as calibration points for molecular dating of ferns.
